\documentclass[letterpaper]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{fontawesome5}

% -------------------- FONT OPTIONS --------------------
% sans-serif
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% serif
% \usepackage{charter}

% \pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in} % Default was -.5in
\addtolength{\textheight}{1in}


\urlstyle{same}


\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-3pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Subsection formatting
\titleformat{\subsection}{
  \vspace{-4pt}\scshape\raggedright\large
}{\hspace{-0.15in}}{0em}{}[\color{black}\vspace{-8pt}]

% % Ensure that generate pdf is machine readable/ATS parsable
% \pdfgentounicode=1

% -------------------- CUSTOM COMMANDS --------------------
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSkillPoint}[2]{
    \item
    \begin{tabularx}{0.99\textwidth}{>{\raggedright}p{2.5cm}X}
        \textbf{#1} & #2 \\
    \end{tabularx}\vspace{-6pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\setlength{\footskip}{4.08003pt}

% -------------------- START OF DOCUMENT --------------------
\begin{document}

% -------------------- HEADING--------------------
\vspace{-8pt}

\begin{center}
   {\Huge\scshape{Siddartha Muppalla} }\\ \vspace{3pt}
    \small
    {\faMapMarker}
     $  $ Mechanicsburg, PA $  $
    {\faIcon{phone}}
    {+1(385)313-5989} $  $
    {\faIcon{envelope}}
    \href{mailto:siddartha.muppalla@gmail.com}
    {\underline{siddartha.muppalla@gmail.com}} $  $
    {\faIcon{linkedin}}
    \href{https://linkedin.com/in/siddartha-muppalla}{\underline{siddartha-muppalla}}$  $
    % {\faIcon{globe}}
    % \href{https://siddartha-muppalla.netlify.app/}{\underline{Portfolio}} $  $
            \faIcon{github}
    \href{https://github.com/siddarthamuppalla}{\underline{siddarthamuppalla}} $  $
    
\end{center}

% -------------------- EDUCATION --------------------
\vspace{-15pt}
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Utah}{\small{Aug 2022 - Dec 2023}}
      {Master of Science - Information Systems }{GPA: 4.0/4.0}
      % \vspace{2pt}
      
      \small{Relevant Courses:} Java \& Data Structures, Algorithms, System Architecture \& Design, Security, Object-Oriented Programming

  \resumeSubHeadingListEnd


 % -------------------- EXPERIENCE --------------------
 \vspace{-5pt}
\section{Professional Experience}
  \resumeSubHeadingListStart
      \resumeProjectHeading
      {\textbf{Software Engineer Intern} $|$ \textbf{CognoWiz} $|$\footnotesize\emph{ Herndon, Virginia}\vspace{1pt}}{\small{Dec 2023 – Present}}
        \resumeItemListStart
            
            % \resumeItem{Revamped multi-threading design in .NET MVVM framework, which improved the application’s performance by 40\%.}
            % \vspace{-12pt}
 
            % \resumeItem{Utilized RESTful web services to retrieve dynamic content from backend databases and crafted new APIs.}
            % \resumeItem{Developed web applications using Java, Spring Boot, Maven, Kafka, PostgreSQL, and React.js  contributing to the implementation of new features, enhancements and automated test in a test-driven development environment.}
            \resumeItem{Developed and shipped new features, enhancements and automated tests for web applications using Java, Spring Boot, Maven, Kafka, PostgreSQL, and React.js.}
            % \resumeItem{Successfully managed the complete lifecycle of various IT applications, ensuring seamless delivery and integration within customer organizations.}
            
            \resumeItem{Collaborated with cross-functional teams to establish comprehensive API documentation using Swagger, enhancing clarity and ease of integration for both internal and external stakeholders.}
            \resumeItem{Led end-to-end development of critical features from architecture to deployment, ensuring seamless integration with existing systems and enhancing overall product functionality.}
            % \resumeItem{Facilitated seamless integration between internal and external stakeholders by crafting meticulous API documentation with Swagger, reducing integration time by 30\% and enhancing process clarity.}
            \resumeItem{Skilled in understanding and interpreting complex requirements through effective communication, probing for information, and facilitating consensus among stakeholders.}

            \resumeItem{Enhanced payment processing capabilities through seamless integration of third-party APIs, resulting in a 25\% improvement in checkout conversion rates and a \$50K increase in monthly revenue}
            

      \resumeItemListEnd
      
      \resumeProjectHeading
      {\textbf{Software Engineer Intern} $|$ \textbf{Oracle} $|$\footnotesize\emph{ Salt Lake City, Utah}\vspace{1pt}}{\small{Jan 2023 – Sep 2023}}
        \resumeItemListStart
            \resumeItem{Created a full-stack web application for customer tracking that improved month-on-month revenue by \$2M.}
            \resumeItem{Employed a tech stack encompassing Node.js, Express, jQuery, React.js, MongoDB, Passport.js and OAuth2.0.}
            \resumeItem{Developed and maintained project plans, timelines, and budgets for application delivery projects.}
            % \resumeItem{Designed a scalable and performant database schema in MongoDB for handling millions of records.}

            \resumeItem{Implemented robust authentication and authorization using OAuth, ensuring restricted access to sensitive data.}
            \resumeItem{Successfully co-led application lifecycle from design to deployment, fostering cross-functional teamwork. }
            \resumeItem{Established targeted test suites with Jest, resulting in a quantifiable 15\% improvement in code coverage.}
      \resumeItemListEnd
          
    \resumeProjectHeading
      {\textbf{Software Engineer} $|$ \textbf{Deloitte} $|$ \footnotesize\emph{Hyderabad, India}\vspace{1pt}}{\small{Jun 2021 – Jul 2022}}
        \resumeItemListStart 
        
            \resumeItem{Engineered application backend using Java, Spring Boot, Spring MVC, Spring AOP ensuring high user satisfaction.}

            % \resumeItem{Optimized data flow with Hibernate ORM, reducing query times by 20\% for improved data management.}
            % \resumeItem{Created spring boot microservices that consumed and processed data from different enterprise applications using SNS/SQS and stored the data in DynamoDB.}
            \resumeItem{Created spring boot microservices for processing high volumes of transaction data from enterprise applications using SNS/SQS for messaging and DynamoDB for reliable storage, which improved data processing efficiency by 30\%. .}
            \resumeItem{Designed and implemented secure and scalable RESTful APIs on AWS API Gateway, reducing response time by 20\%.}

            % \resumeItem{Implemented an event-driven email notification system using Kafka and Spring Kafka, handling order notifications effortlessly.}
            % \vspace{-12pt}           
            \resumeItem{Containerized microservices using Docker and automated deployments with Jenkins CI/CD pipelines on AWS ECS.}
            \resumeItem{Improved code quality and maintainability by establishing a rigorous test-driven development (TDD) process using JUnit and Mockito, increasing code coverage by 20\% and reducing bug incidence by 10\%.
            }

            
      \resumeItemListEnd
 % \vspace{-12pt}

      \resumeProjectHeading
      {\textbf{Associate Software Developer} $|$ \textbf{ClearTax} $|$ \footnotesize\emph{Bengaluru, India}\vspace{1pt}}{\small{Jul 2020 – Jun 2021}}
        \resumeItemListStart 
        
      \resumeItem{Developed and maintained a scalable SaaS application using React and Node.js., ensuring robust performance and reliability.}
      
    % \resumeItem{Built responsive frontend components using React.js and efficiently managed application state using Redux.}
\resumeItem{Collaborated with seniors to proactively identify and fix production bugs 10\% faster, increasing application uptime to 99.9\%.}
% \resumeItem{Collaborated with senior engineers to proactively identify and resolve production bugs 10\% faster, increasing application uptime to 99.9\%.}
 % \vspace{-12pt}

% \resumeItem{Architected  reusable middleware to streamline ERP integrations with ClearTax APIs, reducing integration time by 40\%. }

\resumeItem{Architected and built modular middleware solutions for ERP integration with ClearTax APIs, resulting in a 50\% improvement in integration scalability and maintainability.}
\resumeItem{Leveraged code reviews and mentorship to enhance troubleshooting, debugging and problem-solving strategies. }
      \resumeItemListEnd
          
    \resumeSubHeadingListEnd 

% -------------------- SKILLS --------------------
\vspace{-5pt}
\section{Skills}
 \begin{itemize}[leftmargin=0.05 in, label={}]
    \small{
     \resumeSkillPoint{\textbf{Programming}}{: Java, Spring Boot, Node.js, Python, JavaScript, TypeScript, React, HTML5, CSS3, SQL, PostgreSQL, MongoDB} \\

     % \resumeSkillPoint{\textbf{Web Tech}}{: } \\
    %  \resumeSkillPoint{\textbf{Databases}}{: PostgreSQL, Oracle, MySQL, MongoDB} \\
     \resumeSkillPoint{\textbf{Cloud}}{: AWS (EC2, Lambda, API Gateway, S3, DynamoDB, RDS, ECS), GCP BigQuery} \\
    %  \resumeSkillPoint{\textbf{Tools \& IDE}}{: Eclipse IDE, Visual Studio, IntelliJ, Maven, Postman, Jira, Lucid Chart} \\
     \resumeSkillPoint{\textbf{Outros}}{: Agile, Scrum, Git, Jenkins, Terraform, Kafka, Docker, Jest, Junit, Kubernetes, DevOps, Linux, CI/CD} \\}
 \end{itemize}


% -------------------- CERTIFICATIONS --------------------
\vspace{-5pt}
\section{Professional Certifications}
    \resumeItemListStart 
    \small{
        \resumeItem{AWS Certified Developer - Associate} \vspace{-3pt}
        \resumeItem{GCP(Google Cloud) Certified Associate Cloud Engineer}\vspace{-3pt}
        \resumeItem{Certified ScrumMaster}\vspace{-3pt}
        }
    \resumeItemListEnd

% -------------------- PROJECTS --------------------
% \vspace{-5pt}
\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading
      {\textbf{Taxonomy — Patient Appointment Scheduling System} $|$ 
      {\faIcon{link}}$ $
      \underline{\href{https://medium.com/@siddartha.muppalla/provider-taxonomy-patient-appointment-scheduler-a1538c10f7c0}{Blog}}\vspace{1pt}}{\small{May 2023}}
        \resumeItemListStart
            \resumeItem{Designed an optimized system architecture for an application that manages provider data and scheduling operations at the University of Utah Hospital. Proposed the high-level system design solution to the team developing the real-world application.}
            % \resumeItem{Proposed the high-level system design to the team developing the real-world application.}
            \resumeItemListEnd
            
            \vspace{5pt}
      \resumeProjectHeading
      {\textbf{UAV Localization using Modified Penguin Search Optimization Algorithm} $|$ 
      {\faIcon{link}}$ $
      \underline{\href{https://doi.org/10.1016/j.compeleceng.2023.108757}{Publication}}\vspace{1pt}}{\small{Jun 2023}}
        \resumeItemListStart
            \resumeItem{Using Python, implemented UAV localization using Modified Penguin Search Optimization Algorithm}
            \resumeItem{Achieved lowest estimation error when compared against other nature inspired algorithms.}
      \resumeItemListEnd
    \end{itemize}
      

\end{document}
